Models of lens candidates from Space Warps CFHTLS

### 2017-03-20 parts/massmodel.tex
edits to intro

The mass will naturally depend on the lens and source redshifts, which
are unknown when a lens candidate is first identified.  But this is
not a problem, because a model can be trivially rescaled to use better
redshift values, as and when they become available.  This work applies
photometric redshifts from the CFHTLS pipeline to the candidate
lensing galaxies.  Source redshifts are set to $z=2$ unless an
unambiguous photometric redshift is available.

>>>>

The mass will naturally depend on the lens and source redshifts, which
are unknown when a lens candidate is first identified.  But this is
not a problem, because a model can be trivially rescaled to use better
redshift values, as and when they become available.  This work applies
photometric redshifts from the CFHTLS pipeline to the candidate
lensing galaxies; the values range from $z=0.2$ to $z=1$ (see
Table~\ref{tab:models}).  Source redshifts are set to $z=2$ unless an
unambiguous photometric redshift is available.  The mass normalisation
depends only weakly on the source redshift, provided it is not close
to the lens redshift.
